Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-07-29 paper/main.tex
remove abstract and insert todo

%###################################################################################################
\begin{abstract}
    \textbf{!TODO!}
    This paper establishes the basis for a novel individual-based mechanical model of rod-shaped
    bacteria.
    It describes methods of how to obtain data from microscopic images such that they can be used
    for parameter estimation purposes.
    Furthermore, we show initial results for parameter estimates and an application of the model to
    the formation of multilayers within bacterial colonies.
\end{abstract}

>>>>

%###################################################################################################
\begin{abstract}
    \textbf{TODO: ABSTRACT}
    % This paper establishes the basis for a novel individual-based mechanical model of rod-shaped
    % bacteria.
    % It describes methods of how to obtain data from microscopic images such that they can be used
    % for parameter estimation purposes.
    % Furthermore, we show initial results for parameter estimates and an application of the model to
    % the formation of multilayers within bacterial colonies.
\end{abstract}
